### 2023-12-21 sections/4-results.tex
updated knn plots
added radio-ml plots with knn throughput
using scientific notation for throughput in results tables
updated up to greedy sieve in methods

\caption{Local fractal dimension vs. cluster depth, grouped by decile of LFD, across six datasets.}
\end{figure}
%% end LFD plots

Figures~\ref{fig:plots:fashion-mnist-scaling}A, ~\ref{fig:plots:glove-25-scaling}B, and ~\ref{fig:plots:sift-scaling}C show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance. 
Figure~\ref{fig:plots:random-scaling}D shows the scaling behavior of CAKES on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
The horizontal axis in each figure denotes the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axis denotes throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in our Supplement section. In these plots, we label the recall at each scale for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall at all scales.

Tables \ref{table:results:ann-fashion}, \ref{table:results:ann-glove-25}, \ref{table:results:ann-sift}, and \ref{table:results:ann-random} show the throughput and recall of CAKES's algorithms at each cardinality multiplier (i.e., scale) for the fashion-mnist, glove-25, sift, and random datasets respectively. When reporting recall, we use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider
only three decimal places.
Figures~\ref{fig:plots:fashion-mnist-scaling}A, ~\ref{fig:plots:glove-25-scaling}B, and ~\ref{fig:plots:sift-scaling}C show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance. 
Figure~\ref{fig:plots:random-scaling}D shows the scaling behavior of CAKES on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
The horizontal axis in each figure denotes the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axis denotes throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in our Supplement section. In these plots, we label the recall at each scale for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall at all scales.

@@

\begin{figure}
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
\subcaption{Silva for $k=10$.    }
\label{fig:results:silva-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/radioml-knn-10.png}
\subcaption{RadioML for $k=10$.
}
\label{fig:results:radioml-scaling}
\end{subfigure}%

@@

% We need to redo this plot so that we do not actually augment random datasets but instead take larger and larger 
% random datasets
% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/random-1000000-128-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on a random dataset for $k=10$.
%     }
%     \label{fig:results:random-scaling}
% \end{figure}

@@

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the fashion-mnist dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1 & 13330.275 & 0.954 & 2191.849 & 0.950 & 212.602 & 1.000 & 2009.483 & 1.000 & 2167.365 & 1.000 \\
                    \hline
                    2 & 13822.528 & 0.803 & 2118.513 & 0.927 & 106.372 & 1.000 & 939.169 & 1.000 & 1141.225 & 1.000 \\
                    \hline
                    4 & 16648.524 & 0.681 & 2043.628 & 0.898 & 53.077 & 1.000 & 461.016 & 0.997 & 982.117 & 1.000 \\
                    \hline
                    8 & 16785.981 & 0.525 & 1925.593 & 0.857 & 26.577 & 1.000 & 225.827 & 0.995 & 1179.813 & 1.000 \\
                    \hline
                    16 & 18717.175 & 0.494 & 1841.863 & 0.862 & 13.292 & 1.000 & 116.960 & 0.991 & 1201.409 & 1.000 \\
                    \hline
                    32 & 15597.778 & 0.542 & 1850.943 & 0.775 & 6.647 & 1.000 & 59.148 & 0.985 & 1157.667 & 1.000 \\
                    \hline
                    64 & 14997.277 & 0.378 & 1787.142 & 0.677 & 3.324 & 1.000 & 26.068 & 0.968 & 1102.849 & 1.000 \\
                    \hline
                    128 & 14866.019 & 0.357 & 1659.660 & 0.538 & 1.662 & 1.000 & 13.265 & 0.964 & 1039.607 & 1.000 \\
                    \hline
                    256 & -- & -- & 1597.264 & 0.592 & 0.831 & 1.000 & 6.650 & 0.962 & 1058.972 & 1.000 \\
                    \hline
                    512 & -- & -- & 1826.362 & 0.581 & 0.416 & 1.000 & 3.563 & 0.949 & 1035.260 & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the glove-25 dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1 & 22755.175 & 0.801 & 2829.338 & 0.835 & 278.176 & 1.000 & 2378.006 & 1.000 & 722.326 & 1.000 \\
                    \hline
                    2 & 23792.690 & 0.607 & 2701.804 & 0.832 & 139.414 & 1.000 & 1188.398 & 1.000 & 574.516 & 1.000 \\
                    \hline
                    4 & 24990.630 & 0.443 & 2609.474 & 0.839 & 69.813 & 1.000 & 619.241 & 1.000 & 625.208 & 1.000 \\
                    \hline
                    8 & 27843.055 & 0.294 & 2514.357 & 0.834 & 34.878 & 1.000 & 302.683 & 1.000 & 592.699 & 1.000 \\
                    \hline
                    16 & 31114.062 & 0.213 & 2225.654 & 0.885 & 17.437 & 1.000 & 150.971 & 1.000 & 549.073 & 1.000 \\
                    \hline
                    32 & 32423.543 & 0.178 & 2008.537 & 0.764 & 8.701 & 1.000 & 74.016 & 0.999 & 475.266 & 1.000 \\
                    \hline
                    64 & -- & -- & 1990.317 & 0.631 & 4.362 & 1.000 & 37.735 & 0.997 & 461.066 & 1.000 \\
                    \hline
                    128 & -- & -- & -- & -- & 2.176 & 1.000 & 18.960 & 0.998 & 440.758 & 1.000 \\
                    \hline
                    256 & -- & -- & -- & -- & 1.067 & 1.000 & 9.472 & 0.998 & 422.591 & 1.000 \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the sift dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1 & 19330.282 & 0.782 & 3977.432 & 0.686 & 72.610 & 1.000 & 697.809 & 1.000 & 551.894 & 1.000 \\
                    \hline
                    2 & 20319.372 & 0.552 & 3800.401 & 0.614 & 36.237 & 1.000 & 329.950 & 1.000 & 265.615 & 1.000 \\
                    \hline
                    4 & 21765.007 & 0.394 & 3686.606 & 0.637 & 18.152 & 1.000 & 165.175 & 1.000 & 142.545 & 1.000 \\
                    \hline
                    8 & 24796.528 & 0.298 & 3582.099 & 0.710 & 9.077 & 1.000 & 77.187 & 1.000 & 79.353 & 1.000 \\
                    \hline
                    16 & 26760.717 & 0.210 & 3498.893 & 0.690 & 4.539 & 1.000 & 39.809 & 1.000 & 81.172 & 1.000 \\
                    \hline
                    32 & 27522.668 & 0.193 & 3435.058 & 0.639 & 2.269 & 1.000 & 20.910 & 0.999 & 78.124 & 1.000 \\
                    \hline
                    64 & -- & -- & 3391.916 & 0.678 & 1.135 & 1.000 & 8.867 & 0.997 & 74.344 & 1.000 \\
                    \hline
                    128 & -- & -- & 3363.965 & 0.643 & 0.566 & 1.000 & 4.786 & 0.993 & 68.005 & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on a random dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1 & 11713.738 & 0.060 & 4283.182 & 0.028 & 71.575 & 1.000 & 733.821 & 1.000 & 553.948 & 1.000 \\
                    \hline
                    2 & 10061.864 & 0.048 & 4043.999 & 0.021 & 36.157 & 1.000 & 358.083 & 1.000 & 269.314 & 1.000 \\
                    \hline
                    4 & 9120.868 & 0.031 & 3639.337 & 0.014 & 18.072 & 1.000 & 189.802 & 1.000 & 137.236 & 1.000 \\
                    \hline
                    8 & 8352.077 & 0.022 & 3371.923 & 0.013 & 9.036 & 1.000 & 88.375 & 1.000 & 56.871 & 1.000 \\
                    \hline
                    16 & 8250.619 & 0.008 & 3174.156 & 0.006 & 4.531 & 1.000 & 43.613 & 1.000 & 26.136 & 1.000 \\
                    \hline
                    32 & -- & -- & 3013.970 & 0.007 & 2.270 & 1.000 & 17.201 & 1.000 & 13.534 & 1.000 \\
                    % \hline
                    % 64 & -- & -- & -- & -- & 1.135 & 1.000 & 9.939 & 1.000 & 0.000 & 0.000 \\
                    % \hline
                    % 128 & --& -- & -- & -- & 0.567 & 1.000 & 5.106 & 1.000 & 0.000 & 0.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

>>>>

    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of LFD and weighted by the cardinalities of the clusters.}
    \label{fig:results:lfd-plots}
\end{figure}
%% end LFD plots

Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance. 
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
The horizontal axis in each figure denotes the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axis denotes throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in our Supplement section. In these plots, we label the recall at each scale for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall at all scales.

Tables \ref{table:results:ann-fashion}, \ref{table:results:ann-glove-25}, \ref{table:results:ann-sift}, and \ref{table:results:ann-random} show the throughput and recall of CAKES's algorithms at each cardinality multiplier (i.e., scale) for the fashion-mnist, glove-25, sift, and random datasets respectively. When reporting recall, we use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider
only three decimal places.
Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance. 
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
The horizontal axis in each figure denotes the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axis denotes throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in our Supplement section. In these plots, we label the recall at each scale for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall at all scales.

@@

\begin{figure}
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-knn-10.png}
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
\subcaption{Silva for $k=10$.    }
\label{fig:results:silva-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/radio-ml-knn-10.png}
\subcaption{RadioML for $k=10$ at SnR = 10dB.
}
\label{fig:results:radioml-scaling}
\end{subfigure}%

@@

% We need to redo this plot so that we do not actually augment random datasets but instead take larger and larger 
% random datasets
% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/random-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on a random dataset for $k=10$.
%     }
%     \label{fig:results:random-scaling}
% \end{figure}

@@

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the fashion-mnist dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.13~$\times10^{2}$  & 1.000 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 1.06~$\times10^{2}$  & 1.000 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 5.31~$\times10^{1}$  & 1.000 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.66~$\times10^{1}$  & 1.000 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.33~$\times10^{1}$  & 1.000 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 6.65~$\times10^{0}$  & 1.000 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 3.32~$\times10^{0}$  & 1.000 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.66~$\times10^{0}$  & 1.000 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 8.31~$\times10^{-1}$ & 1.000 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 4.16~$\times10^{-1}$ & 1.000 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the glove-25 dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.78~$\times10^{2}$ & 1.000 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.39~$\times10^{2}$ & 1.000 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.98~$\times10^{1}$ & 1.000 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.49~$\times10^{1}$ & 1.000 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000 \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.74~$\times10^{1}$ & 1.000 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000 \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 8.70~$\times10^{0}$ & 1.000 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 4.36~$\times10^{0}$ & 1.000 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & --                  & --    & 2.18~$\times10^{0}$ & 1.000 & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & --                  & --    & 1.07~$\times10^{0}$ & 1.000 & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000 \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the sift dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 7.26~$\times10^{1}$  & 1.000 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.62~$\times10^{1}$  & 1.000 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.82~$\times10^{1}$  & 1.000 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 9.08~$\times10^{0}$  & 1.000 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 4.54~$\times10^{0}$  & 1.000 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.27~$\times10^{0}$  & 1.000 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 1.14~$\times10^{0}$  & 1.000 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 5.66~$\times10^{-1}$ & 1.000 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on a random dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-random}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.16~$\times10^{1}$ & 1.000 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\
                    \hline
                    2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.62~$\times10^{1}$ & 1.000 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\
                    \hline
                    4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.81~$\times10^{1}$ & 1.000 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\
                    \hline
                    8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 9.04~$\times10^{0}$ & 1.000 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\
                    \hline
                    16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.53~$\times10^{0}$ & 1.000 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\
                    \hline
                    32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 2.27~$\times10^{0}$ & 1.000 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\
                    % \hline
                    % 64 & -- & -- & -- & -- & 1.135 & 1.000 & 9.939 & 1.000 & 0.000 & 0.000 \\
                    % \hline
                    % 128 & --& -- & -- & -- & 0.567 & 1.000 & 5.106 & 1.000 & 0.000 & 0.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}
